Meta-learning in movement prediction problem of aperiodic time-series data

### 2025-01-21 doc/thesis/pre_info/acknowledge.tex
ack, title, ref stuff

I would like to thank everyone in Maezono and Hongo laboratory, fellow students and the laboratory staff, for helping me out whenever I run into trouble with the administrative documents or health.

>>>>

In addition, I would like to thank everyone in Maezono and Hongo laboratory, fellow students and the laboratory staff, for helping me out whenever I run into trouble with the administrative documents or health.
